Generating and modifying matrices

### 2019-04-16 Analysis/Character_difference/02-Modifying_matrices.Rmd
Updated analysis

## Seed for repeatability
set.seed(0)
```

@@

```{r, fig.width=12, fig.height=6}
## Character difference
char_diff_matrix_maxi <- char.diff(matrix_maxi)
par(mfrow = c(1, 2))
## The character difference density (per character)
plot(char_diff_matrix_maxi, type = "density", main = "Maximised matrix")
## The character difference matrix (pairwise)
plot(char_diff_matrix_maxi, type = "matrix")
```

```{r, fig.width=12, fig.height=6}
## Character difference
char_diff_matrix_mini <- char.diff(matrix_mini)
par(mfrow = c(1, 2))
## The character difference density (per character)
plot(char_diff_matrix_mini, type = "density", main = "Minimised matrix")
## The character difference matrix (pairwise)
plot(char_diff_matrix_mini, type = "matrix")
```

```{r, fig.width=12, fig.height=6}
## Character difference
char_diff_matrix_rand <- char.diff(matrix_rand)
par(mfrow = c(1, 2))
## The character difference density (per character)
plot(char_diff_matrix_rand, type = "density", main = "Randomised matrix")
## The character difference matrix (pairwise)
plot(char_diff_matrix_rand, type = "matrix")
```

@@

```{r, fig.width=12, fig.height=12, eval = FALSE, echo = FALSE}
pdf("../../Writing/Figures/Modif_matrix.pdf", width = 7.2, height = 4.5)
par(mfrow = c(2, 3), bty = "n", mar = c(1,1,1,1))
## Tree
plot(tree, cex = 0.8, main = "A - Simulated tree")
## Normal matrix
plot(char_diff_matrix_norm, type = "matrix", main = "B - Normal matrix", legend = FALSE)
## Empty plot
plot(0,0, col = "white", xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")
## Maximised matrix
plot(char_diff_matrix_maxi, type = "matrix", main = "C - Maximised matrix", legend = FALSE)
## Minimised matrix
plot(char_diff_matrix_mini, type = "matrix", main = "D - Minimised matrix", legend = FALSE)
## Randomised matrix
plot(char_diff_matrix_rand, type = "matrix", main = "E - Randomised matrix", legend = FALSE)
dev.off()
```

>>>>

## Seed for repeatability
set.seed(123)
```

@@

```{r, fig.width=12, fig.height=6}
## Character difference
char_diff_matrix_maxi <- char.diff(matrix_maxi[[1]])
par(mfrow = c(1, 2))
## The character difference density (per character)
plot(char_diff_matrix_maxi, type = "density", main = "Maximised matrix")
## The character difference matrix (pairwise)
plot(char_diff_matrix_maxi, type = "matrix")
```

```{r, fig.width=12, fig.height=6}
## Character difference
char_diff_matrix_mini <- char.diff(matrix_mini[[1]])
par(mfrow = c(1, 2))
## The character difference density (per character)
plot(char_diff_matrix_mini, type = "density", main = "Minimised matrix")
## The character difference matrix (pairwise)
plot(char_diff_matrix_mini, type = "matrix")
```

```{r, fig.width=12, fig.height=6}
## Character difference
char_diff_matrix_rand <- char.diff(matrix_rand[[1]])
par(mfrow = c(1, 2))
## The character difference density (per character)
plot(char_diff_matrix_rand, type = "density", main = "Randomised matrix")
## The character difference matrix (pairwise)
plot(char_diff_matrix_rand, type = "matrix")
```

@@

```{r, fig.width=12, fig.height=12, eval = FALSE, echo = FALSE}
# pdf("../../Writing/Figures/Modif_matrix.pdf", width = 7.2, height = 4.5)
par(mfrow = c(2, 3), bty = "n", mar = c(1,1,1,1))
## Tree
plot(tree, cex = 0.8, main = "A - Simulated tree")
## Normal matrix
plot(char_diff_matrix_norm, type = "matrix", main = "B - Normal matrix", legend = FALSE)
## Empty plot
plot(0,0, col = "white", xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")
## Maximised matrix
plot(char_diff_matrix_maxi, type = "matrix", main = "C - Maximised matrix", legend = FALSE)
## Minimised matrix
plot(char_diff_matrix_mini, type = "matrix", main = "D - Minimised matrix", legend = FALSE)
## Randomised matrix
plot(char_diff_matrix_rand, type = "matrix", main = "E - Randomised matrix", legend = FALSE)
dev.off()
```
